---
title: "Students Stress and Well Being Survey Analysis"
format: 
  docx:
     toc: true
     toc-depth: 1
     number-sections: true
     highlight-style: github
     fig-align: center
     tbl-cap-location: top
---

```{r setup, include=FALSE}

library(dplyr)
library(dslabs)
library(tidyverse)
library(gtsummary)
library(flextable)
library(knitr)
library(kableExtra)
library(psych)
library(car)
library(ggfortify)
library(broom)
library(skimr)
library(scales)
library(rstatix)
library(ggpubr)
library(report)
library(janitor)
library(psych)
library(GPArotation)


# data <- read.csv("Stress Dataset.csv",stringsAsFactors = TRUE)

data <- RKaggle::get_dataset("ashutoshsingh22102/stress-and-well-being-data-of-college-students")

# str(data)

#replace blanks with NA
data[data == ""] <- NA

#recode gender for interpretability
data <- data %>% mutate(gender_recode = case_when(
  Gender==1 ~ "Female", 
  Gender==0 ~ "Male") ) 

#check if it is a factor
data$gender_recode <- as.factor(data$gender_recode)

#check which factors to use
summary(data$Age)

#recode age into a categorical variable
data <- data %>% mutate(age_category = case_when(
  Age <= 19 & Age >=10 ~ "10-19 years", 
  Age <= 29 & Age >=20 ~ "20-29 years",
  Age <= 39 & Age >=30 ~ "30-39 years", 
  Age <= 49 & Age >=40 ~ "40-49 years",
  Age <= 59 & Age >=50 ~ "50-59 years", 
  Age <= 69 & Age >=60 ~ "60-69 years",
  Age <= 79 & Age >=70 ~ "70-79 years", 
  Age <= 89 & Age >=80 ~ "80-89 years",
  Age <= 99 & Age >=90 ~ "90-99 years", 
  Age <= 109 & Age >=100 ~ "100-109 years") ) 

#ensure it is a factor
data$age_category <- as.factor(data$age_category)

levels(data$`Which type of stress do you primarily experience?`)

data$`Which type of stress do you primarily experience?`
# recode stress variable for readability
data <- data %>% mutate(stress_type = case_when(
  `Which type of stress do you primarily experience?` ==  "Distress (Negative Stress) - Stress that causes anxiety and impairs well-being." ~ "Negative Stress", 
  `Which type of stress do you primarily experience?` ==  "Eustress (Positive Stress) - Stress that motivates and enhances performance." ~ "Positive Stress",
  `Which type of stress do you primarily experience?` ==  "No Stress - Currently experiencing minimal to no stress." ~ "No Stress") ) 


# data quality
# skim(data)

#clean names
data_clean <- clean_names(data)

```


# Results

The dataset was downloaded from Kaggle (1) using the url:
https://www.kaggle.com/datasets/ashutoshsingh22102/stress-and-well-being-data-of-college-students/data



# Table 1 – Demographic characteristics of survey respondents

```{r, echo=FALSE, warning=FALSE}

data_clean %>% tbl_summary(by=stress_type,
                     include = c(gender_recode, age, age_category),
    type = list(all_continuous() ~ "continuous2"),
digits = list(all_categorical()~c(0,1) , 
                all_continuous()~1) ,
    statistic = list(all_continuous() ~ c( "{mean} ({sd})") ) ,
    missing = "ifany",
    missing_text = "Unknown",
    missing_stat = "{N_miss} ({p_miss}%)") %>%
  bold_labels() %>%
   remove_row_type(type =  "level",level_value = "") %>% 
  as_flex_table() %>% 
   flextable::set_table_properties(width=1,layout="autofit", 
                       opts_word = list(repeat_headers=TRUE,
                                        keep_with_next=TRUE)) %>% 
   flextable::font(fontname="Times New Roman", part="all") %>% 
   flextable::line_spacing(space=1, part="all")
  

```


# Table 2 – Likert Scale Characteristics of respondents

```{r, echo=FALSE, warning=FALSE}

all <- data_clean %>% 
  dplyr::select(have_you_recently_experienced_stress_in_your_life,
                have_you_noticed_a_rapid_heartbeat_or_palpitations,
                have_you_been_dealing_with_anxiety_or_tension_recently,
                do_you_face_any_sleep_problems_or_difficulties_falling_asleep,
                have_you_been_dealing_with_anxiety_or_tension_recently_1,
                have_you_been_getting_headaches_more_often_than_usual,
                do_you_get_irritated_easily,
                do_you_have_trouble_concentrating_on_your_academic_tasks,
                have_you_been_feeling_sadness_or_low_mood,
                have_you_been_experiencing_any_illness_or_health_issues,
                do_you_often_feel_lonely_or_isolated,
                do_you_feel_overwhelmed_with_your_academic_workload,
                are_you_in_competition_with_your_peers_and_does_it_affect_you,
                do_you_find_that_your_relationship_often_causes_you_stress,
                are_you_facing_any_difficulties_with_your_professors_or_instructors,
                is_your_working_environment_unpleasant_or_stressful,
                do_you_struggle_to_find_time_for_relaxation_and_leisure_activities,
                is_your_hostel_or_home_environment_causing_you_difficulties,
                do_you_lack_confidence_in_your_academic_performance,
                do_you_lack_confidence_in_your_choice_of_academic_subjects,
                academic_and_extracurricular_activities_conflicting_for_you,
                do_you_attend_classes_regularly,
                have_you_gained_lost_weight
                )


all_numeric <- as.data.frame(lapply(all, function(x) as.numeric(as.character(x))))

all_numeric %>%
  mutate(across(
    everything(), # Applies to all columns
    ~ factor(
      .x,
      levels = c(1, 2, 3, 4, 5),
      labels = c("Not at all","Slightly","Moderately","Very","Extremely"),
      ordered = TRUE
    )
  )) %>% pivot_longer(
    cols = everything(), 
    names_to = "Likert Item", 
    values_to = "Response")  %>%
  mutate(`Likert Item` = factor(`Likert Item`, levels = unique(`Likert Item`))) %>%
  tbl_cross(
    row = `Likert Item`,
    col = Response,
    percent = "row", 
    margin = NULL) %>%
  bold_labels() %>% 
  as_flex_table() %>%
  # Apply Times New Roman to the entire table (body and header)
   flextable::set_table_properties(width=1,layout="autofit", 
                       opts_word = list(repeat_headers=TRUE,
                                        keep_with_next=TRUE)) %>% 
   flextable::font(fontname="Times New Roman", part="all") %>% 
   flextable::line_spacing(space=1, part="all")

```


# Table 3 - Characteristics of all Respondents. 

A stress score was created based on all questions. The overall reliability was found to be 0.7, which is acceptable by standard convention. 

```{r, echo=FALSE, warning=FALSE}

score <- data_clean %>% dplyr::select(have_you_recently_experienced_stress_in_your_life,
                have_you_noticed_a_rapid_heartbeat_or_palpitations,
                have_you_been_dealing_with_anxiety_or_tension_recently,
                do_you_face_any_sleep_problems_or_difficulties_falling_asleep,
                have_you_been_dealing_with_anxiety_or_tension_recently_1,
                have_you_been_getting_headaches_more_often_than_usual,
                do_you_get_irritated_easily,
                do_you_have_trouble_concentrating_on_your_academic_tasks,
                have_you_been_feeling_sadness_or_low_mood,
                have_you_been_experiencing_any_illness_or_health_issues,
                do_you_often_feel_lonely_or_isolated,
                do_you_feel_overwhelmed_with_your_academic_workload,
                are_you_in_competition_with_your_peers_and_does_it_affect_you,
                do_you_find_that_your_relationship_often_causes_you_stress,
                are_you_facing_any_difficulties_with_your_professors_or_instructors,
                is_your_working_environment_unpleasant_or_stressful,
                do_you_struggle_to_find_time_for_relaxation_and_leisure_activities,
                is_your_hostel_or_home_environment_causing_you_difficulties,
                do_you_lack_confidence_in_your_academic_performance,
                do_you_lack_confidence_in_your_choice_of_academic_subjects,
                academic_and_extracurricular_activities_conflicting_for_you,
                do_you_attend_classes_regularly,
                have_you_gained_lost_weight) %>% rowSums(na.rm=TRUE) 


data_clean2 <- data_clean %>% mutate(score = score)

data_clean2_subset <- data_clean2 %>% select(-c(age, gender, gender_recode, age_category, which_type_of_stress_do_you_primarily_experience, stress_type))


all_stats_df <- psych::alpha(data_clean2_subset)$total %>% t() %>% signif(digits=3) %>% as.data.frame()

all_stats_df <- cbind(Variable = rownames(all_stats_df), all_stats_df) 


flextable(all_stats_df)  %>% 
   flextable::set_table_properties(width=1,layout="autofit", 
                       opts_word = list(repeat_headers=TRUE,
                                        keep_with_next=TRUE)) %>% 
  flextable::font(fontname="Times New Roman", part="all") %>% colformat_double(digits = 2) 





all_item_stats_df <- psych::alpha(data_clean2_subset)$item.stats %>%  signif(digits=3) %>% as.data.frame()

  
all_item_stats_df <- cbind(Variable = rownames(all_item_stats_df), all_item_stats_df) 


flextable(all_item_stats_df)  %>% 
   flextable::set_table_properties(width=1,layout="autofit", 
                       opts_word = list(repeat_headers=TRUE,
                                        keep_with_next=TRUE)) %>% 
  flextable::font(fontname="Times New Roman", part="all") %>% colformat_double(digits = 2) 



```

# Pre defined factors 

The reliability of the groups of indicators, stated in another study (5) were assessed. These included: 
- Emotional and Stress Indicators
- Physical and Health Indicators
- Academic & Environment Stressors
- Social & Relationship Factors


```{r, echo=FALSE, warning=FALSE}

emotional_stress <- data_clean2[,c("have_you_recently_experienced_stress_in_your_life",
                "have_you_noticed_a_rapid_heartbeat_or_palpitations",
                "have_you_been_dealing_with_anxiety_or_tension_recently",
                "do_you_face_any_sleep_problems_or_difficulties_falling_asleep",
                "do_you_have_trouble_concentrating_on_your_academic_tasks",
                "have_you_been_feeling_sadness_or_low_mood",
                "do_you_get_irritated_easily",
                "do_you_often_feel_lonely_or_isolated")]

# psych::alpha(emotional_stress) #0.5379649


physical_health <- data_clean2[, c(
                "have_you_been_getting_headaches_more_often_than_usual",
                "have_you_been_experiencing_any_illness_or_health_issues",
                "have_you_gained_lost_weight")]

# psych::alpha(physical_health) #	0.225059


academic_environment <- data_clean2[, c(
                "do_you_feel_overwhelmed_with_your_academic_workload",
                "are_you_in_competition_with_your_peers_and_does_it_affect_you",
                "do_you_lack_confidence_in_your_academic_performance",
                 "do_you_lack_confidence_in_your_choice_of_academic_subjects",
                "academic_and_extracurricular_activities_conflicting_for_you",
                "do_you_attend_classes_regularly",
                "are_you_facing_any_difficulties_with_your_professors_or_instructors",
                "is_your_working_environment_unpleasant_or_stressful",
                "is_your_hostel_or_home_environment_causing_you_difficulties")]

# psych::alpha(academic_environment ) #0.5934446	

social_relationships <- data_clean2[, c(
                "do_you_find_that_your_relationship_often_causes_you_stress",
                "do_you_struggle_to_find_time_for_relaxation_and_leisure_activities" )]

# psych::alpha(social_relationships ) #0.2215781


alphas <- rbind(psych::alpha(emotional_stress)$total[1],
      psych::alpha(physical_health)$total[1],
      psych::alpha(academic_environment)$total[1],
      psych::alpha(social_relationships)$total[1])


factors <- rbind("emotional_stress","physical_health","academic_environment",
                 "social_relationships")

alpha1 <- cbind(factors = factors, alpha = round(alphas,2))  
rownames(alpha1) <- c("1","2","3","4")
alpha1 %>% flextable()



```

Some of the categories, have low reliability, less than 0.7.


# Factor Analysis

Factor Analysis was then used to see if there were other subscales / groups of questions corresponding to themes. 

```{r, echo=FALSE, warning=FALSE}



fa_data <- data_clean2[, c("have_you_recently_experienced_stress_in_your_life",
                "have_you_noticed_a_rapid_heartbeat_or_palpitations",
                "have_you_been_dealing_with_anxiety_or_tension_recently",
                "do_you_face_any_sleep_problems_or_difficulties_falling_asleep",
                "have_you_been_dealing_with_anxiety_or_tension_recently_1",
                "have_you_been_getting_headaches_more_often_than_usual",
                "do_you_get_irritated_easily",
                "do_you_have_trouble_concentrating_on_your_academic_tasks",
                "have_you_been_feeling_sadness_or_low_mood",
                "have_you_been_experiencing_any_illness_or_health_issues",
                "do_you_often_feel_lonely_or_isolated",
                "do_you_feel_overwhelmed_with_your_academic_workload",
                "are_you_in_competition_with_your_peers_and_does_it_affect_you",
                "do_you_find_that_your_relationship_often_causes_you_stress",
                "are_you_facing_any_difficulties_with_your_professors_or_instructors",
                "is_your_working_environment_unpleasant_or_stressful",
                "do_you_struggle_to_find_time_for_relaxation_and_leisure_activities",
                "is_your_hostel_or_home_environment_causing_you_difficulties",
                "do_you_lack_confidence_in_your_academic_performance",
                "do_you_lack_confidence_in_your_choice_of_academic_subjects",
                "academic_and_extracurricular_activities_conflicting_for_you",
                "do_you_attend_classes_regularly",
                "have_you_gained_lost_weight")]


fa_data  <- as.data.frame(lapply(fa_data , function(x) as.numeric(as.character(x)))) 

# Remove rows with missing data (none)
fa_data <- na.omit(fa_data) 

ev <- eigen(cor(fa_data)) # get eigenvalues
# ev$values

# scree(fa_data, pc=FALSE) #gives approx 3 factors 


#factor analysis assumptions

#Kaiser-Meyer-Olkin (KMO) Measure of Sampling Adequacy
KMO(fa_data) #Overall MSA =  0.71

# cor(fa_data)

# Bartlett's Test of Sphericity
cortest.bartlett(fa_data)$p.value 
# p=0 means items are significantly correlated).


#how many factors
# run parallel analysis
parallel <- fa.parallel(fa_data, fm = "pa", fa = "fa")

#Parallel analysis suggests that the number of factors =  6  and the number of components =  NA 

# assuming constructs do not overlap on one another - varimax
fa_model <- fa(fa_data, nfactors = 6, fm = "pa", rotate = "varimax")

# Print the results clearly, hiding weak loadings under 0.30
print(fa_model, cut = 0.30, sort = TRUE) 


loads <- fa_model$loadings

fa.diagram(loads)

capture.output(print(print(fa_model, cut = 0.30, sort = TRUE, digits=2))) %>% writeLines( "factor_analysis_output.txt")

# dim(fa_model$loadings)

factorloadings <- round(round(fa_model$loadings[ 1:23,], 6), 2)

write.csv(factorloadings, file="factor_loadings.csv")

# factorloadings %>% kable()

```


# Reevaluate Reliability - cross check

```{r, echo=FALSE, warning=FALSE}

environment <- fa_data[ , c( "is_your_working_environment_unpleasant_or_stressful",
 "are_you_facing_any_difficulties_with_your_professors_or_instructors",
 "are_you_in_competition_with_your_peers_and_does_it_affect_you",
 "do_you_feel_overwhelmed_with_your_academic_workload",
 "do_you_often_feel_lonely_or_isolated",
 "do_you_struggle_to_find_time_for_relaxation_and_leisure_activities",
 "do_you_find_that_your_relationship_often_causes_you_stress"

)]


depression <- fa_data[ , c( "do_you_have_trouble_concentrating_on_your_academic_tasks",
 "have_you_been_feeling_sadness_or_low_mood",
 "do_you_get_irritated_easily",
 "have_you_been_getting_headaches_more_often_than_usual",
 "have_you_been_experiencing_any_illness_or_health_issues"

)]


anxiety <- fa_data[ , c( "have_you_noticed_a_rapid_heartbeat_or_palpitations",
 "have_you_recently_experienced_stress_in_your_life",
 "have_you_been_dealing_with_anxiety_or_tension_recently"
)]


# have_you_been_getting_headaches_more_often_than_usual
sleep <- fa_data[ , c( "have_you_been_dealing_with_anxiety_or_tension_recently_1",
 "do_you_face_any_sleep_problems_or_difficulties_falling_asleep"

)]

academic <- fa_data[ , c( "academic_and_extracurricular_activities_conflicting_for_you",
 "do_you_lack_confidence_in_your_choice_of_academic_subjects"

)]


confidence <- fa_data[ , c( "do_you_lack_confidence_in_your_academic_performance",
 "is_your_hostel_or_home_environment_causing_you_difficulties"

)]


alphas2 <- rbind(psych::alpha(anxiety)$total[1],
      psych::alpha(academic)$total[1],
      psych::alpha(sleep)$total[1],
      psych::alpha(environment)$total[1],
      psych::alpha(depression)$total[1],
      psych::alpha(confidence)$total[1])


factors2 <- rbind("anxiety","academic","sleep","environment","depression","confidence")


# cbind(factors2, alpha = round(alphas2,2))


alpha2 <- cbind(factors = factors2, alpha = round(alphas2,2))  
rownames(alpha2) <- c("1","2","3","4","5","6")
alpha2 %>% flextable()



```

# Recalculating Scores for the new subscales /factors in the dataset

```{r, echo=FALSE, warning=FALSE, message=FALSE}
# add scores to the orignal dataset

anxiety <- data_clean2 %>% dplyr::select(have_you_noticed_a_rapid_heartbeat_or_palpitations,
have_you_recently_experienced_stress_in_your_life,
have_you_been_dealing_with_anxiety_or_tension_recently) %>% rowSums(na.rm=TRUE) 

academic <- data_clean2 %>% dplyr::select(academic_and_extracurricular_activities_conflicting_for_you,
do_you_lack_confidence_in_your_choice_of_academic_subjects) %>% rowSums(na.rm=TRUE) 

sleep <- data_clean2 %>% dplyr::select(have_you_been_dealing_with_anxiety_or_tension_recently_1,
do_you_face_any_sleep_problems_or_difficulties_falling_asleep) %>% rowSums(na.rm=TRUE) 

environment <- data_clean2 %>% dplyr::select(is_your_working_environment_unpleasant_or_stressful,
are_you_facing_any_difficulties_with_your_professors_or_instructors,
are_you_in_competition_with_your_peers_and_does_it_affect_you,
do_you_feel_overwhelmed_with_your_academic_workload,
do_you_often_feel_lonely_or_isolated,
do_you_struggle_to_find_time_for_relaxation_and_leisure_activities,
do_you_find_that_your_relationship_often_causes_you_stress) %>% rowSums(na.rm=TRUE) 

depression <- data_clean2 %>% dplyr::select(do_you_have_trouble_concentrating_on_your_academic_tasks,
have_you_been_feeling_sadness_or_low_mood,
do_you_get_irritated_easily,
have_you_been_getting_headaches_more_often_than_usual,
have_you_been_experiencing_any_illness_or_health_issues) %>% rowSums(na.rm=TRUE) 

confidence <- data_clean2 %>% dplyr::select(do_you_lack_confidence_in_your_academic_performance,
is_your_hostel_or_home_environment_causing_you_difficulties) %>% rowSums(na.rm=TRUE) 


data_clean3 <- data_clean2 %>% mutate(anxiety = anxiety,
                                      academic = academic,
                                      sleep = sleep,
                                      environment = environment,
                                      depression = depression,
                                      confidence = confidence) 

data_clean3_subset <- data_clean3 %>% select(-c(age, gender, gender_recode, age_category, which_type_of_stress_do_you_primarily_experience, stress_type, score))



all_stats_df2 <- psych::alpha(data_clean3_subset)$total %>% t() %>% signif(digits=3) %>% as.data.frame()

all_stats_df2 <- cbind(Variable = rownames(all_stats_df2), all_stats_df2) 


flextable(all_stats_df2)  %>% 
  flextable::set_table_properties(width=1,layout="autofit", 
                                  opts_word = list(repeat_headers=TRUE,
                                                   keep_with_next=TRUE)) %>% 
  flextable::font(fontname="Times New Roman", part="all") %>% colformat_double(digits = 2) 



all_item_stats_df2 <- psych::alpha(data_clean3_subset)$item.stats %>%  signif(digits=3) %>% as.data.frame()


all_item_stats_df2 <- cbind(Variable = rownames(all_item_stats_df2), all_item_stats_df2) 

dim(all_item_stats_df2)


flextable(all_item_stats_df2[24:29,])  %>% 
  flextable::set_table_properties(width=1,layout="autofit", 
                                  opts_word = list(repeat_headers=TRUE,
                                                   keep_with_next=TRUE)) %>% 
  flextable::font(fontname="Times New Roman", part="all") %>% colformat_double(digits = 2) 
```


# Score Distribution

Evalutating normality of the dataset. According to the QQ plot, the data seems normal, following the straight line through the origin, there is slight deviation on the tails. 

The histogram however, shows there are some outliers. 

```{r, echo=FALSE, warning=FALSE}
hist(data_clean3$score,
     main = "Stress Score",
     xlab = "Stress Score",            
     ylab = "Number of Responses",                  
     breaks = 10,                                    
     las = 1)        

shapiro.test(data_clean3$score)


qqPlot(data_clean3$score)


ggplot(data_clean3) +
  aes(x = "", y = score) +
  geom_boxplot(fill = "steelblue") +
  theme_minimal()


```


# Score Distribution - Extreme outlier removal

score 115 shows an extreme outlier which was removed

```{r, echo=FALSE, warning=FALSE}

data_clean3 %>% identify_outliers(score) %>% select(score, is.outlier, is.extreme) %>% flextable()

# test by removing extremes 

data_clean4 <- data_clean3 %>% filter(score != c(115))

hist(data_clean4$score,
     main = "Stress Score",
     xlab = "Stress Score",            
     ylab = "Number of Responses",                  
     breaks = 10,                                    
     las = 1)        

shapiro.test(data_clean4$score)


qqPlot(data_clean4$score)




```

# Linear Regression - Satisfaction Score

```{r, echo=FALSE, warning=FALSE}
data_subset <- data_clean4 %>% select(age, gender_recode, stress_type,
                              anxiety, academic, sleep, environment, depression, confidence, score) %>%
  mutate(age_cleaned = scale(age, center = TRUE, scale = FALSE)) %>%
  select(-age)


model <- lm(score ~ ., data = data_subset)

report(model)

```



# Assumptions

```{r, echo=FALSE, warning=FALSE}

autoplot(model)

```

# Reporting Beta table

```{r, echo=FALSE, warning=TRUE}

tbl_regression(model,pvalue_fun = label_style_pvalue(digits = 3),
                            estimate_fun = label_style_number(digits=3)) %>%
                            bold_p() %>%
  as_flex_table() %>%
   flextable::set_table_properties(width=1,layout="autofit",
                       opts_word = list(repeat_headers=TRUE,
                                        keep_with_next=TRUE)) %>%
  flextable::font(fontname="Times New Roman", part="all") %>%
  flextable::line_spacing(space=1, part="all")
```

# Reporting ANOVA Table

```{r, echo=FALSE, warning=TRUE}


anova_results <- car::Anova(model, type="II" )


 anova_results %>%
   tidy() %>%
   flextable() %>%
   colformat_double(j = c("sumsq","statistic", "p.value"), digits = 3) %>%
   set_header_labels(
     term = "Variable",
     sumsq = "Sum of Squares",
     df = "df",
     statistic = "F statistic",
     p.value = "p-value"
   ) %>%
   bold(i = ~ p.value < 0.05, j = "p.value") %>%
   flextable::set_table_properties(width = 1,
                        layout = "autofit",
                        opts_word = list(repeat_headers = TRUE, keep_with_next = TRUE)) %>%
  flextable::font(fontname = "Times New Roman", part = "all") %>%
   flextable::line_spacing(space = 1, part = "all")


 report(anova_results)
```




# R package References 

```{r, echo=FALSE, warning=FALSE}
report(sessionInfo())

```

# References

1.	Stress and Well-being Data of College Students [Internet]. [cited 2026 Oct 3]. Available from: https://www.kaggle.com/datasets/ashutoshsingh22102/stress-and-well-being-data-of-college-students
2.	Machine Learning Algorithms for Detecting Mental Stress in College Students | IEEE Conference Publication | IEEE Xplore [Internet]. [cited 2026 Oct 3]. Available from: https://ieeexplore.ieee.org/abstract/document/10544243
3.	Optimizing Well-Being: Unveiling Eustress and Distress through Machine Learning | IEEE Conference Publication | IEEE Xplore [Internet]. [cited 2026 Oct 3]. Available from: https://ieeexplore.ieee.org/abstract/document/10544592
4.	Ovi MSI, Hossain J, Rahi MRA, Akter F. Protecting Student Mental Health with a Context-Aware Machine Learning Framework for Stress Monitoring [Internet]. arXiv; 2025 [cited 2026 Oct 3]. Available from: http://arxiv.org/abs/2508.01105 doi:10.48550/arXiv.2508.01105
5.	Student Stress Monitoring Datasets [Internet]. [cited 2026 Oct 3]. Available from: https://www.kaggle.com/datasets/mdsultanulislamovi/student-stress-monitoring-datasets
6.	Brown S. Likert Scale Examples for Surveys.
7.	8  Cleaning data and core functions – The Epidemiologist R Handbook [Internet]. [cited 2026 Oct 3]. Available from: https://www.epirhandbook.com/en/new_pages/cleaning.html#column-names
8.	RPubs - A Primer on Factor Analysis in Resear using Reproducible R Software [Internet]. [cited 2026 Oct 3]. Available from: https://rpubs.com/Geesaale/1064415
9.	EBSCO [Internet]. [cited 2026 Oct 3]. Cronbach’s alpha | Science | Research Starters | EBSCOhost. Available from: https://www.ebsco.com/
10.	17  Descriptive tables – The Epidemiologist R Handbook [Internet]. [cited 2026 Oct 3]. Available from: https://www.epirhandbook.com/en/new_pages/tables_descriptive.html#dplyr-package
11.	Stats and R [Internet]. [cited 2026 Oct 3]. ANOVA in R. Available from: https://statsandr.com/blog/anova-in-r/
12.	Comparison tests/methods available — tests [Internet]. [cited 2026 Oct 3]. Available from: https://www.danieldsjoberg.com/gtsummary/reference/tests.html
13.	neversaint. How to change legend title in ggplot [Forum post]. Stack Overflow [Internet]. 2022 [cited 2026 Oct 3]. Available from: https://stackoverflow.com/q/14622421
14.	MASH. Guides: MASH : Maths and Stats Help: Cronbach’s Alpha (R) [Internet]. [cited 2026 Oct 3]. Available from: https://guides.library.lincoln.ac.uk/mash/cronbachs_alpha_R


